Computing volume via non-linear rectangular prisms

### 2019-08-14 Cav2D/article-template.tex
finished single cavalieri section

\section{Cavalieri Integral}
The single Cavalieri integral was originally defined in \cite{ackermann12} without having to resort to vector calculus. In this section we will define the Cavalieri integral using vector calculus. As the reader will undoubtedly realize, if we define the single Cavalieri integral using vector calculus then it becomes trivial to
extend its definition into $\mathbb{R}^3$.\\

@@

\noindent
Let $R$ denote the region which is bounded by $f(x,y)$, $\mathbf{c}(t)+\left <a,0\right >$, $\mathbf{c}(t)+\left <b,0\right >$ and the $x$-axis. Let the $A_R$ denote 
the area of $R$. We can approximate $A_R$ with:
\begin{equation}
 \label{eq:caval1}
 \int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1,
 \end{equation}
Let us verify that this is indeed the case:
 \begin{itemize}
  \item $\Delta x_i^1 = x_{i+1}^1 - x_i^1$ represents the width of a non-rectangular integration strip.
  \item $f(x_i^2)$ represents the height of a non-rectangular integration strip.
  \item $f(x_i^2)\Delta x_i^1$ represents the area of a non-rectangular integration strip (due to Cavalieri's principle).
  \item The Cavalieri sum $\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1$, therefore, approximates the area of $R$.
  \item In the limit the Cavalieri sum, therefore, approaches the area of $R$.
 \end{itemize}

>>>>

\section{Cavalieri Integral}
The single Cavalieri integral was originally defined in \cite{ackermann12} without having to resort to vector calculus. In this section we will redefine the Cavalieri integral using vector calculus notation. As the reader will undoubtedly realize, if we define the single Cavalieri integral using vector calculus then it becomes trivial to
extend its definition into $\mathbb{R}^3$.\\

@@

\noindent
Let $R$ denote the region which is bounded by $f(x,y)$, $\mathbf{c}(t)+\left <a,0\right >$, $\mathbf{c}(t)+\left <b,0\right >$ and the $x$-axis. Let the $A_R$ denote 
the area of $R$. We can approximate $A_R$ with:
\begin{equation}
 \label{eq:caval1}
 A_R \approx \sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1,
 \end{equation}
Let us verify that this is indeed the case:
 \begin{itemize}
  \item $\Delta x_i^1 = x_{i+1}^1 - x_i^1$ represents the width of a non-rectangular integration strip.
  \item $f(x_i^2)$ represents the height of a non-rectangular integration strip.
  \item $f(x_i^2)\Delta x_i^1$ represents the area of a non-rectangular integration strip (due to Cavalieri's principle).
  \item The Cavalieri sum $\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1$, therefore, approximates the area of $R$.
  \item In the limit the Cavalieri sum, therefore, approaches the area of $R$.
 \end{itemize}

\noindent
The aforementioned limit is known as Cavalieri integral and in this paper we denote this integral as follows:

\begin{equation}
\label{eq:cav_1d}
\int \limits_{\mathcal{C}} f(x)~dx = \lim_{n \rightarrow \infty}  \sum_{i=0}^{n-1} f(x_i^2) \Delta x_i^1,
\end{equation}
with $\mathcal{C} = \{\mathbf{c}(t),[a,b]\}$. Equation~\eqref{eq:cav_1d} is difficult to evaluate in its current form. Luckily, the Cavalieri integral 
can be converted into an equivalent Riemann integral using the transformation $h$:
 \begin{equation}
 \int \limits_{\mathcal{C}} f(x)\, dx = \int_{a}^{b} f\circ h(x)~dx. 
\end{equation}

\noindent
The only thing that now remains is to find an expression for $h$. Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b] \times [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
\begin{equation}
 \label{eq:pat_rel_1d}
 \left <x_i^2,f(x_i^2) \right > = \left <x_i^1,0 \right> + \left<c_x(t),c_y(t) \right >.
 \end{equation}
 We can rewrite Equation~\eqref{eq:pat_rel_1d} as
 \begin{equation}
 \label{eq:t_func_1d}
 c_y(t) = f(x_i^1 + c_x(t)).
 \end{equation}
 We can now solve for $t$ in Equation~\eqref{eq:t_func_1d} in terms of $x_i^1$. If we substitute the solution $t(x_i)$ so obtained into Equation~\ref{eq:pat_rel_1d} we obtain 
\begin{equation}
\label{eq:h_func_1d}
 x_i^2 = h(x_i^1) = x_i^1 + c_x\circ t(x_i^1).
\end{equation}

\noindent
Note, the Cavalieri integral is denoted in \cite{ackermann12} via:
\begin{equation}
\label{eq:cav_1d}
\int_{a(y)}^{b(y)} f(x)~dx = \lim_{n \rightarrow \infty}  \sum_{i=0}^{n-1} f(x_i^2) \Delta x_i^1,
\end{equation}
where $a(y)$ denotes the functional representation of $\mathbf{c}(t) + \left <a,0 \right >$ and $b(y) = a(y)+(b-a)$.
